\documentclass[a4paper, 10pt, oneside]{report}
\usepackage{graphicx}
\graphicspath{ {images/} }


\usepackage[textwidth = 200mm,margin = 15mm]{geometry}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{longtable}
\setcounter{secnumdepth}{3}


\title{COS301: Application and Functional Requirements}
\date{2015-02-27}
\author{Group 3B}


\begin{document}

\maketitle
\pagenumbering{gobble}

\newpage
\pagenumbering{roman}

\tableofcontents 

\newpage
\pagenumbering{arabic}


\chapter{Introduction}

Github URL: \url{https://github.com/u12026442/group3b_men_at_work.git}
\\
\\
This document contains the architecture and functional requirements for the Buzz Discussion Board system. It will start with a brief  vision and background to explain the need for such a system from where the architecture and functional requirements will follow.


\chapter{Vision}

The user interface.
\\
\\
For the user interface we plan to make use of web application as well as a mobile application that will access that buzz system. The user will be presented with a login screen on start-up of the application. After successfully logging in the user will enter their profile. They will then receive all the groups that they are a part of and all the posts that they have not looked at will be marked. They will then be able to access the spaces, threads and replies for the groups that they are a part of as well as contribute to the groups according to their permission level.

\chapter{Background}

\textit "A general discussion of what lead to the project including potentially:"

\begin{itemize}
\item \textit business/research opportunities,
\item \textit opportunities to simplify/improve some aspect of life/work or community,
\item \textit problems your client is currently facing,
\item \textit ...
\end{itemize}

\chapter{ Functional requirements and application design}
	\section{Use case prioritization}
		\subsection{Critical}
		\subsection{Important}
		\subsection{Nice to have}
	\section{Use case/Services contracts}

\newpage
\include{groups}
\newpage
\include{spaces}
\newpage
\include{threads}
\newpage
\include{replies}
\newpage
\include{user}
\newpage
\include{userlist}
\newpage
\include{userinterface}
\newpage
%\include{authenticate}
%\newpage
\include{audit}
\newpage
\include{report}
\newpage
\include{XP}
\newpage

\section{Required functionality}
\section{Process specifications}
\section{Domain Model}
\section{Open Issues}



\end{document}

